Pipeline Performance Figure Generation

### 2023-05-31 TestingPipeline/Scripts/paper_figure_generation.Rmd
Fixing prop_in_common figure.

for (i in c(0,1)){
  for (j in c(0,1)){
    for (k in c(0,1)){
      for (l in c(0,1)){
        for (m in c(0,1)){
          for (n in c(0,1)){
            combos_list$toolcombo[p] <- paste(i,j,k,l,m,n)
            combos_list$toolcombo2[p] <- paste(if(i){"tnv"}else{"0"},if(j){"DVF"}else{"0"},
                                               if(k){"tv"}else{"0"},if(l){"VB"}else{"0"},
                                               if(m){"VS"}else{"0"},if(n){"VS2"}else{"0"})
            combos_list$tune_not_viral[p] <- i
            combos_list$DVF[p] <- j
            combos_list$tune_viral[p] <- k
            combos_list$VIBRANT[p] <- l
            combos_list$VS[p] <- m
            combos_list$VS2[p] <- n
            p <- p+1
          }
        }
      }
    }
  }
}

@@

@@

@@

ann_colors = list(
  num_vir=magma(100),
  tnv = c("black", pal(6)[1]),
  tv = c("black", pal(6)[3]),
  dvf = c("black", pal(6)[2]),
  vb = c("black", pal(6)[4]),
  vs = c("black", pal(6)[5]),
  vs2 = c("black", pal(6)[6])
)

@@

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = viridis(100),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common.png",
                  annotation_legend = F)
```

>>>>

@@

rownames(prop_high_viruses) <- combos_list$toolcombo
colnames(prop_high_viruses) <- combos_list$toolcombo

combos_list$ruletype <- "other"
combos_list$ruletype[combos_list$toolcombo %in% c("0 0 1 0 0 1",
                                          "0 0 1 1 0 0",
                                          "0 0 0 1 0 0")] <- "high precision"
combos_list$ruletype[combos_list$toolcombo %in% c("1 1 0 0 1 1",
                                          "1 1 0 1 1 1",
                                          "1 1 0 0 0 1",
                                          "1 1 0 1 0 1")] <- "high recall"
combos_list$ruletype[combos_list$toolcombo %in% c("0 0 1 0 0 1",
                                          "0 1 1 0 0 1",
                                          "0 0 0 0 0 1",
                                          "1 0 1 1 0 1",
                                          "1 0 1 0 1 1",
                                          "1 0 1 0 0 1")] <- "high MCC"
#combos_lists$ruletype[accuracy_scores$toolcombo %in% c("0 0 1 0 0 1")] <- "high MCC and high precision"
combos_list$ruletype[combos_list$toolcombo %in% c("1 1 1 1 1 1")] <- "all"

combos_list$ruletype <- as.factor(combos_list$ruletype)
```

@@

ann_col = data.frame(
    tnv = combos_list$tune_not_viral,
    tv = combos_list$tune_viral,
    dvf = combos_list$DVF,
    vb = combos_list$VIBRANT,
    vs = combos_list$VS,
    vs2 = combos_list$VS2,
    ruleset_type = combos_list$ruletype
)

@@

ann_colors = list(
  num_vir=magma(100),
  tnv = c("black", pal(6)[1]),
  tv = c("black", pal(6)[3]),
  dvf = c("black", pal(6)[2]),
  vb = c("black", pal(6)[4]),
  vs = c("black", pal(6)[5]),
  vs2 = c("black", pal(6)[6]),
  ruleset_type = c("all" = magma(7)[3],
                   "high MCC" = magma(7)[4],
                   "high precision" = magma(7)[5],
                   "high recall" = magma(7)[6], 
                   "other" = "grey")
)

@@

pheatmap::pheatmap(prop_high_viruses,
                  annotation_row = ann_row,
                  annotation_col=ann_col,
                  annotation_colors = ann_colors,
                  border_color = "black",
                  color = viridis(100),
                  cutree_rows = 3,
                  cutree_cols = 3,
                  show_rownames = F,
                  show_colnames = F,
                  filename = "../IntermediaryFiles/pheatmap_prop_viruses_in_common.png",
                  annotation_legend = T)
```
